---
title: "Analyse Gruppe 1"
params:
  hyp: rig
output:
  html_document: default
  pdf_document: default
---

## start by looking at the data:
 ```{r message=FALSE}
 library(PairedData)
 library(ggplot2)
library(ggpubr)
library(apaTables)
library(papaja)
library(knitr)
library(tidyverse)
library(rstatix)
library(ez)
library(gtools)
library(emmeans)
library(nlme)
library(multcomp)
library(Hmisc)
library(psych)
 
 ```



 ```{r}
dat <- read.csv("data_with_dist_effect_1rpP.csv")
dat_all <-  read.csv("data_cleaned_complete.csv")
dat_accuracy <-  read.csv("data_accuracy.csv") %>% filter(prob_code %in% dat$prob_code)
dat_accuracy_dual <-  read.csv("data_accuracy_p_participant_dual.csv") %>% filter(prob_code %in% dat$prob_code)

dat_demo <- read.csv("data/demo_data.csv") %>% filter(probanden_code %in% dat$prob_code)

dat_all$distance <- factor(dat_all$distance)
dat_all$ordered <- factor(dat_all$ordered,levels=c(TRUE,FALSE)) # change level order so every test does reverse distance first. 
dat_all$mode<- factor(dat_all$mode,levels=c("single","dual_phon","dual_vis","dual_rig")) # change level order so every test does reverse distance first. 
dat_accuracy$ordered <- factor(dat_accuracy$ordered,levels=c(TRUE,FALSE)) # change level order so every test does reverse distance first. 
dat_accuracy$mode<- factor(dat_accuracy$mode,levels=c("single","dual_phon","dual_vis","dual_rig")) # change level order so every test does reverse distance first. 

```

 ```{r}

paste("total participants:",nrow(dat))
options(width=110)
summary(dat_all)


dat_dual_diff <- dat_all %>% filter(mode=="dual_vis")
dat_dual_diff <- dat_dual_diff %>% group_by(prob_code) %>% summarise(dual_diff = (dual_diff[1]))
summary(dat_dual_diff$dual_diff)
range(dat_dual_diff$dual_diff,na.rm=TRUE)
# get the mode:
names(sort(-table(dat_dual_diff$dual_diff)))[1]

dat_dual_diff  %>% gghistogram( x = "dual_diff",
   add = "mean", rug = TRUE,
   palette = "jco") %>% ggpar(xticks.by=1,xlab="difficulty",xlim=c(3,11))



hist(dat_dual_diff$dual_diff)


sd(dat_dual_diff$dual_diff)
dat_dual_diff <- dat_all %>% filter(mode=="dual_phon")
dat_dual_diff <- dat_dual_diff %>% group_by(prob_code) %>% summarise(dual_diff = (dual_diff[1]))
summary(dat_dual_diff$dual_diff)
sd(dat_dual_diff$dual_diff)

dat_dual_diff  %>% gghistogram( x = "dual_diff",
   add = "mean", rug = TRUE,
   palette = "jco") %>% ggpar(xticks.by=1,xlab="difficulty",xlim=c(3,11))

hist(dat_dual_diff$dual_diff)

```

 ```{r }
dat_all %>% mutate(rt_num = rt_num*1000) %>% ggdensity( x = "rt_num",
   add = "mean", rug = TRUE,
   color = "mode", fill = "mode",
   palette = "jco")
dat_all %>% group_by(mode) %>% summarise(mean_rt = mean(rt_num*1000)) %>% select(mode,mean_rt)
 
 ```

# check for practice effect

 ```{r }
ggbarplot(dat_all, x = "trial_number",y = "rt_num",
   add = "mean", rug = TRUE,
#   color = "mode", 
   merge=TRUE,
   palette = "jco") #+ gradient_color("red")
cor_mat <- as.matrix(cbind(dat_all$rt_num,dat_all$trial_number))
rcorr(cor_mat)

# check for practice effect in accuracy data.
dat_trial_n <- dat_all %>% group_by(prob_code,mode) %>% 
    # transform our trial number to number of block
    mutate(block_number = ifelse(trial_number < 48, 1,ifelse(trial_number < 90,2,ifelse(trial_number < 135,3,4)))) %>%
    summarise(block_number = mean(block_number))
dat_acc_trial_n <- dat_accuracy %>% group_by(prob_code,mode) %>% summarise(accuracy = mean(accuracy))
dat_trial_n <- merge(dat_trial_n,dat_acc_trial_n,by=c("prob_code","mode"))
head(dat_trial_n)

dat_trial_n %>% group_by(prob_code) %>% summarise(block_order = paste(block_number[1],block_number[2],block_number[3],block_number[4])) %>% 
    count(block_order)



if(FALSE){

ggbarplot(dat_trial_n, x = "block_number",y = "accuracy",
   add = "mean", rug = TRUE,
   fill= "block_number", 
   merge=TRUE,
   title= "all modes", 
   palette = "jco") + gradient_color("red")
cor_mat <- as.matrix(cbind(dat_trial_n$accuracy,dat_trial_n$block_number))
rcorr(cor_mat)


dat_trial_n_vis <-  dat_trial_n %>% filter(mode %in% c("single", "dual_vis"))
ggbarplot(dat_trial_n_vis, x = "block_number",y = "accuracy",
   add = "mean", rug = TRUE,
   fill= "block_number", 
   merge=TRUE,
   title= "single and vis", 
   palette = "jco") + gradient_color("red")
cor_mat <- as.matrix(cbind(dat_trial_n$accuracy,dat_trial_n$block_number))
rcorr(cor_mat)

dat_trial_n_phon <-  dat_trial_n %>% filter(mode %in% c("single", "dual_phon"))
ggbarplot(dat_trial_n_phon, x = "block_number",y = "accuracy",
   add = "mean", rug = TRUE,
   fill= "block_number", 
   merge=TRUE,
   title= "single and phon", 
   palette = "jco") + gradient_color("red")
cor_mat <- as.matrix(cbind(dat_trial_n$accuracy,dat_trial_n$block_number))
rcorr(cor_mat)

dat_trial_n_rig <-  dat_trial_n %>% filter(mode %in% c("single","dual_rig"))
ggbarplot(dat_trial_n_rig, x = "block_number",y = "accuracy",
   add = "mean", rug = TRUE,
   fill= "block_number", 
   title= "single and RIG", 
   merge=TRUE,
   palette = "jco") + gradient_color("red")
cor_mat <- as.matrix(cbind(dat_trial_n$accuracy,dat_trial_n$block_number))
rcorr(cor_mat)


dat_trial_n <- dat_trial_n %>% group_by(prob_code) %>% summarise(block_order = paste(block_number[1],block_number[2],block_number[3],block_number[4]))
head(dat_trial_n)
}

 ```
 
 ```{r }
 # get descirptives for our participants.

 summary(dat_all)
 dat_all %>% group_by(prob_code) %>% summarise(demo_sex = demo_sex[1]) %>% count(demo_sex)
dat_age <- dat_all %>% group_by(prob_code) %>% summarise(demo_age = demo_age[1]) 
 mean(dat_age$demo_age)
 sd(dat_age$demo_age)
     
dat_all %>% group_by(prob_code) %>% summarise(os = os[1])  %>% count(os)
dat_demo %>% count(Student)
dat_demo %>% count(Studienrichtung)
dat_demo %>% count(Bildungsabschluss)
summary(dat_demo$Mathematiknote)
sd(dat_demo$Mathematiknote)

 ```
 
 ```{r }
 dat_plot <- dat_accuracy %>% group_by(prob_code,mode) %>% summarise(accuracy = mean(accuracy))
ggdensity(dat_plot, x = "accuracy",
   add = "mean", rug = TRUE,
   color = "mode", fill = "mode",
   palette = "jco")

dat_plot %>% group_by(mode) %>% summarise(mean_acc = mean(accuracy))
 
 ```
  ```{r }
ggdensity(dat_accuracy_dual, x = "accuracy",
   add = "mean", rug = TRUE,
   color = "mode", fill = "mode",
   palette = "jco")

dat_accuracy_dual %>% group_by(mode) %>% summarise(mean_acc = mean(accuracy),sd= sd(accuracy))
 
 ```
 
  ```{r }
ggboxplot(dat_all, x = "mode", y = "rt_num",
                color = "mode", palette ="jco"
                , shape = "mode")
 
 ```

 ```{r}
#TODO: check for pratice effect.
#dat_all$datetime <- as.Date(dat_all$datetime)

 # check means and sds so we get an overview.
as.data.frame(t(sapply(dat, function(cl) list(means=mean(cl,na.rm=TRUE), sds=sd(cl,na.rm=TRUE)))))



 ```

# rig: test if there is a difference between participants who did a random interval and those who did not.
 ```{r }

 dat_rig <- dat_all %>% filter(mode == "dual_rig") %>% mutate(rig_random = ifelse(rig_randomness_p < 0.05, 1 , 0)) 
 dat_rig <- dat_rig %>% group_by(prob_code) %>% summarise(mean_rt = mean(rt_num),rig_random=rig_random[1]) 
 ftable(dat_rig$rig_random)

with(dat_rig, t.test(mean_rt~rig_random))

dat_rig$mean_rt = dat_rig$mean_rt * 1000 # get ms

ggbarplot(
          data=dat_rig,
          x="rig_random",
          y="mean_rt",
          add="mean_se",
        fill = "rig_random",
        palette = "jco",
        label=TRUE,
        ,xlab= "RIG task random"
        ,ylab= "reaction time in ms"
          )+ 
    geom_bracket(y.position=1350,xmin=1,xmax=2,label="ns")+
# stat_compare_means(method= "t.test", paired=FALSE,label="p.signif", label.x = 1.5)+ # Add significance levels
    theme_apa()


dat_rig <- dat_rig %>% select(prob_code,rig_random)
dat_acc_rig <- dat_accuracy %>% filter(mode == "dual_rig")  %>% group_by(prob_code) %>% summarise(accuracy = mean(accuracy))

dat_rig <- merge(dat_acc_rig,dat_rig,by="prob_code")
head(dat_rig)

with(dat_rig, t.test(accuracy~rig_random))

ggbarplot(
          data=dat_rig,
          x="rig_random",
          y="accuracy",
          add="mean_se",
        fill = "rig_random",
        label=TRUE,
        palette = "jco",
        ,xlab= "RIG task random"
        ,ylab= "accuracy"
          )+ 
# stat_compare_means(method= "t.test", paired=FALSE,label="p.signif", label.x = 1.5)+ # Add significance levels
    geom_bracket(y.position=1,xmin=1,xmax=2,label="ns")+
    theme_apa()



 ```

# TODO: function for anova
 ```{r }


plot_two_way <- function(data,dep_var="rt_num",indep_vars=c("ordered","distance"),y_label_to_use=NULL,title_to_use=NULL){

    dat <- data 
     
dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered,levels=c(TRUE,FALSE))
desc_plot <- ggbarplot(data=dat,
                       x=indep_vars[1],
                       y=dep_var,fill=indep_vars[2],
                       palette="jco",
                       add="mean_se",
                       position=position_dodge(),
                       ylab=y_label_to_use,
                       label=TRUE,
                       lab.nb.digits=2,
                       lab.pos="out",
                       lab.hjust=-0.4,
                       title=title_to_use) 

if(dep_var == "rt_num"){
desc_plot <-    ggpar(desc_plot,ylim=c(700,1350)) #+ geom_bracket(y.position=1050,x.min="TRUE",xmax="FALSE",label="test")
}

if(dep_var == "accuracy"){
desc_plot <-    ggpar(desc_plot,ylim=c(0.6,1))
}

if(dep_var == "ies"){
desc_plot <-    ggpar(desc_plot,ylim=c(0.5,2.2))
}

return(list( desc_plot=desc_plot))
 }

plot_one_way <- function(data,dep_var="rev_dist_effect_normed",indep_var="mode",y_label_to_use=NULL,title_to_use=NULL){

    dat <- data 
     
desc_plot <- ggbarplot(data=dat,x=indep_var,
                       #label=TRUE,
                       #lab.nb.digits=2,
                       #lab.pos="out",
                       #lab.hjust=-0.4,
                       y=dep_var,fill=indep_var,palette="jco",add="mean_se",position=position_dodge(),ylab=y_label_to_use,title=title_to_use)

return(list( desc_plot=desc_plot))
 }

 ```

# REACTION TIMES: 

## single task:

 ```{r warning=FALSE}


dat <- dat_all %>% filter(mode=="single")


dat$rt_num <- dat$rt_num*1000
my_plot <- plot_two_way(data=dat,dep_var="rt_num",indep_vars=c("ordered","distance"),y_label_to_use="Reaktionszeit in ms",title_to_use="single task")
ez_anova_res <- ezANOVA(data=dat,dv=rt_num,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our reverse distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(mean_rt = mean(rt_num))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( mean_rt ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc


my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position=1350,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position=1350,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])



 ```

## dual phon task:

 ```{r warning=FALSE}
dat <- dat_all %>% filter(mode=="dual_phon")

dat$rt_num <- dat$rt_num*1000
my_plot <- plot_two_way(data=dat,dep_var="rt_num",indep_vars=c("ordered","distance"),y_label_to_use="Reaktionszeit in ms",title_to_use="phonological task")
ez_anova_res <- ezANOVA(data=dat,dv=rt_num,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our reverse distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(mean_rt = mean(rt_num))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( mean_rt ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position=1350,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position=1350,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])





 ```

# dual vis task:

 ```{r warning=FALSE}
dat <- dat_all %>% filter(mode=="dual_vis")

dat$rt_num <- dat$rt_num*1000
my_plot <- plot_two_way(data=dat,dep_var="rt_num",indep_vars=c("ordered","distance"),y_label_to_use="Reaktionszeit in ms",title_to_use="visual task")
ez_anova_res <- ezANOVA(data=dat,dv=rt_num,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our reverse distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(mean_rt = mean(rt_num))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( mean_rt ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position=1350,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position=1350,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])





 ```

# dual rig task:

 ```{r warning=FALSE}
dat <- dat_all %>% filter(mode=="dual_rig")

dat$rt_num <- dat$rt_num*1000
my_plot <- plot_two_way(data=dat,dep_var="rt_num",indep_vars=c("ordered","distance"),y_label_to_use="Reaktionszeit in ms",title_to_use="executive task")
ez_anova_res <- ezANOVA(data=dat,dv=rt_num,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our reverse distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(mean_rt = mean(rt_num))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( mean_rt ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position=1350,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position=1350,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])





 ```

# calc reverse and regular distance effect:


 ```{r warning=FALSE}
dat <- dat_all  %>% group_by(prob_code,mode,ordered,distance) %>% summarise(mean_rt= mean(rt_num,rm.na=TRUE))
dat <- data.frame(dat)
dat$distance <- factor(dat$distance)
dat <- reshape(dat, idvar=c("prob_code","mode","ordered"), timevar = "distance", direction="wide")

dat$rev_dist_effect_rt_normed <- (dat$mean_rt.2 - dat$mean_rt.1)/((dat$mean_rt.2 + dat$mean_rt.1)/2)
dat$dist_effect_rt_normed <- (dat$mean_rt.1 - dat$mean_rt.2)/((dat$mean_rt.2 + dat$mean_rt.1)/2)


 ```
# reverse distance effect anova:

 ```{r warning=FALSE}

 dat_rev <- dat %>% filter(ordered == TRUE)
myplot <- plot_one_way(data=dat_rev,dep_var="rev_dist_effect_rt_normed",indep_var="mode",y_label_to_use="reverse distance effect")
ez_anova_res <- ezANOVA(data=dat_rev,dv=rev_dist_effect_rt_normed,wid=prob_code,within=.(mode),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)
pairwise.t.test(x=dat_rev$dist_effect_rt_normed, g=factor(dat_rev$mode), paired=TRUE, p.adjust.method="BH")

post_hoc <- dat_rev  %>% pairwise_t_test( rev_dist_effect_rt_normed ~ mode, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc


myplot$desc_plot  +
    geom_bracket(y.position=0.07,xmin=1,xmax=2,label=post_hoc$p.adj.signif[1],tip.length=0.001)+
    geom_bracket(y.position=0.075,xmin=1,xmax=3,label=post_hoc$p.adj.signif[2],tip.length=0.001)+
    geom_bracket(y.position=0.08,xmin=1,xmax=4,label=post_hoc$p.adj.signif[3],tip.length=0.001)

#TODO: do this everywhere!


 ```

# distance effect anova:

 ```{r warning=FALSE}

 dat_dist <- dat %>% filter(ordered == FALSE)

plot_one_way(data=dat_dist,dep_var="dist_effect_rt_normed",indep_var="mode",y_label_to_use="distance effect")

ez_anova_res <- ezANOVA(data=dat_dist,dv=dist_effect_rt_normed,wid=prob_code,within=.(mode),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)
pairwise.t.test(x=dat_dist$dist_effect_rt_normed, g=factor(dat_dist$mode), paired=TRUE, p.adjust.method="BH")


 ```





# ACCURACY

## single 

 ```{r warning=FALSE}
dat <- dat_accuracy  %>% filter(mode=="single")
my_plot <- plot_two_way(data=dat,dep_var="accuracy",indep_vars=c("ordered","distance"),y_label_to_use="accuracy",title_to_use="single task")
ez_anova_res <- ezANOVA(data=dat,dv=accuracy,wid=prob_code,within=.(distance,ordered))
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our (reverse) distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(accuracy = mean(accuracy))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( accuracy ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 1,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 1,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])



 ```

## dual_phon 

 ```{r warning=FALSE}
dat <- dat_accuracy  %>% filter(mode=="dual_phon")
my_plot <- plot_two_way(data=dat,dep_var="accuracy",indep_vars=c("ordered","distance"),y_label_to_use="accuracy",title_to_use="phonological task")
ez_anova_res <- ezANOVA(data=dat,dv=accuracy,wid=prob_code,within=.(distance,ordered))
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our (reverse) distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(accuracy = mean(accuracy))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( accuracy ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 1,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 1,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])





 ```

## dual_vis 

 ```{r warning=FALSE}
dat <- dat_accuracy  %>% filter(mode=="dual_vis")
my_plot <- plot_two_way(data=dat,dep_var="accuracy",indep_vars=c("ordered","distance"),y_label_to_use="accuracy",title_to_use="visual task")
ez_anova_res <- ezANOVA(data=dat,dv=accuracy,wid=prob_code,within=.(distance,ordered))
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our (reverse) distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(accuracy = mean(accuracy))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( accuracy ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 1,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 1,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])





 ```

## dual_rig 

 ```{r warning=FALSE}
dat <- dat_accuracy  %>% filter(mode=="dual_rig")
my_plot <- plot_two_way(data=dat,dep_var="accuracy",indep_vars=c("ordered","distance"),y_label_to_use="accuracy",title_to_use="executive task")
ez_anova_res <- ezANOVA(data=dat,dv=accuracy,wid=prob_code,within=.(distance,ordered))
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our (reverse) distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(accuracy = mean(accuracy))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( accuracy ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 1,xmin=0.75,xmax=1.25,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 1,xmin=1.75,xmax=2.25,label=post_hoc$p.adj.signif[2])





 ```

# calc reverse and regular distance effects for accuracy:


 ```{r warning=FALSE}
dat <- dat_accuracy 
dat <- data.frame(dat)
dat$distance <- factor(dat$distance)
dat <- reshape(dat, idvar=c("prob_code","mode","ordered"), timevar = "distance", direction="wide")

# we reverse the effects because for accuracy higher is better. 
dat$rev_dist_effect_acc_normed <- (dat$accuracy.1 - dat$accuracy.2)/((dat$accuracy.2 + dat$accuracy.1)/2)
dat$dist_effect_acc_normed <- (dat$accuracy.2 - dat$accuracy.1)/((dat$accuracy.2 + dat$accuracy.1)/2)


 ```
# reverse distance effect anova:

 ```{r warning=FALSE}

 dat_rev <- dat %>% filter(ordered == TRUE)
myplot <- plot_one_way(data=dat_rev,dep_var="rev_dist_effect_acc_normed",indep_var="mode",y_label_to_use="reverse distance effect (accuracy)")
ez_anova_res <- ezANOVA(data=dat_rev,dv=rev_dist_effect_acc_normed,wid=prob_code,within=.(mode),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)
pairwise.t.test(x=dat_rev$rev_dist_effect_acc_normed, g=factor(dat_rev$mode), paired=TRUE, p.adjust.method="BH")
post_hoc <- dat_rev  %>% pairwise_t_test( rev_dist_effect_acc_normed ~ mode, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

myplot$desc_plot  +
    geom_bracket(y.position=0.21,xmin=1,xmax=2,label=post_hoc$p.adj.signif[1],tip.length=0.001)+
    geom_bracket(y.position=0.23,xmin=1,xmax=3,label=post_hoc$p.adj.signif[2],tip.length=0.001)+
    geom_bracket(y.position=0.25,xmin=1,xmax=4,label=post_hoc$p.adj.signif[3],tip.length=0.001)

 ```

# distance effect anova:

 ```{r warning=FALSE}

 dat_dist <- dat %>% filter(ordered == FALSE)
plot_one_way(data=dat_dist,dep_var="dist_effect_acc_normed",indep_var="mode",y_label_to_use="distance effect (accuracy)")
ez_anova_res <- ezANOVA(data=dat_dist,dv=dist_effect_acc_normed,wid=prob_code,within=.(mode),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)
pairwise.t.test(x=dat_dist$dist_effect_acc_normed, g=factor(dat_dist$mode), paired=TRUE, p.adjust.method="BH")

 ```


# Calc IES and reverse distance effect for IES: 

IES =  RT  / ACCURACY

 ```{r warning=FALSE,message=FALSE}

dat <- dat_all  %>% group_by(prob_code,mode,ordered,distance) %>% summarise(mean_rt= mean(rt_num,rm.na=TRUE))
dat_ies <- merge(data.frame(dat_accuracy),data.frame(dat),by=c("prob_code","ordered","distance","mode"))
dat_ies <- dat_ies %>% mutate(ies = mean_rt/accuracy)

# correlation for speed acc tradeoff
cor_mat <- as.matrix(cbind(dat_ies$mean_rt,dat_ies$accuracy))
rcorr(cor_mat)

```

## single task:

 ```{r warning=FALSE}
dat <- dat_ies %>% filter(mode=="single")


my_plot <- plot_two_way(data=dat,dep_var="ies",indep_vars=c("ordered","distance"),title_to_use="single task")
ez_anova_res <- ezANOVA(data=dat,dv=ies,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our (reverse) distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(ies = mean(ies))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( ies ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 2.2,xmin=0.75,xmax=1.25,tip.length= 0.01,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 2.2,xmin=1.75,xmax=2.25,tip.length= 0.01,label=post_hoc$p.adj.signif[2])





 ```

## dual phon task:

 ```{r warning=FALSE}
dat <- dat_ies %>% filter(mode=="dual_phon")

my_plot <- plot_two_way(data=dat,dep_var="ies",indep_vars=c("ordered","distance"),title_to_use="phonological task")
ez_anova_res <- ezANOVA(data=dat,dv=ies,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our (reverse) distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(ies = mean(ies))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( ies ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 2.2,xmin=0.75,xmax=1.25,tip.length= 0.01,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 2.2,xmin=1.75,xmax=2.25,tip.length= 0.01,label=post_hoc$p.adj.signif[2])





 ```

# dual vis task:

 ```{r warning=FALSE}
dat <- dat_ies %>% filter(mode=="dual_vis")

my_plot <- plot_two_way(data=dat,dep_var="ies",indep_vars=c("ordered","distance"),title_to_use="visual task")
ez_anova_res <- ezANOVA(data=dat,dv=ies,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# checḱ for (reverse) distance effect
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(ies = mean(ies))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( ies ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 2.2,xmin=0.75,xmax=1.25,tip.length= 0.01,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 2.2,xmin=1.75,xmax=2.25,tip.length= 0.01,label=post_hoc$p.adj.signif[2])





 ```

# dual rig task:

 ```{r warning=FALSE}
dat <- dat_ies %>% filter(mode=="dual_rig")

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
my_plot <- plot_two_way(data=dat,dep_var="ies",indep_vars=c("ordered","distance"),title_to_use="executive task")
ez_anova_res <- ezANOVA(data=dat,dv=ies,wid=prob_code,within=.(distance,ordered),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

dat$distance <- factor(dat$distance)
dat$ordered <- factor(dat$ordered)
# now check for our (reverse) distance effect: 
dat <- dat %>% group_by(prob_code,ordered,distance) %>% summarise(ies = mean(ies))
post_hoc <- dat %>% group_by(ordered) %>% pairwise_t_test( ies ~ distance, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc

my_plot$desc_plot 

my_plot$desc_plot + 
    geom_bracket(y.position= 2.2,xmin=0.75,xmax=1.25,tip.length= 0.01,label=post_hoc$p.adj.signif[1])+
    geom_bracket(y.position= 2.2,xmin=1.75,xmax=2.25,tip.length= 0.01,label=post_hoc$p.adj.signif[2])







 ```

# calc reverse and regular distance effect:

 ```{r warning=FALSE}

dat <- reshape(data.frame(dat_ies), idvar=c("prob_code","mode","ordered"), timevar = "distance", direction="wide")

dat$rev_dist_effect_ies_normed <- (dat$ies.2 - dat$ies.1)/((dat$ies.2 + dat$ies.1)/2)
dat$dist_effect_ies_normed <- (dat$ies.1 - dat$ies.2)/((dat$ies.2 + dat$ies.1)/2)


 ```
# reverse distance effect anova:

 ```{r warning=FALSE}

 dat_rev <- dat %>% filter(ordered == TRUE)
myplot <- plot_one_way(data=dat_rev,dep_var="rev_dist_effect_ies_normed",indep_var="mode",y_label_to_use="reverse distance effect (ies)")
ez_anova_res <- ezANOVA(data=dat_rev,dv=rev_dist_effect_ies_normed,wid=prob_code,within=.(mode),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)
pairwise.t.test(x=dat_rev$dist_effect_ies_normed, g=factor(dat_rev$mode), paired=TRUE, p.adjust.method="BH")

post_hoc <- dat_rev  %>% pairwise_t_test( rev_dist_effect_ies_normed ~ mode, paired = TRUE, p.adjust.method = "bonferroni") 
post_hoc


myplot$desc_plot  +
    geom_bracket(y.position=0.26,xmin=1,xmax=2,label=post_hoc$p.adj.signif[1],tip.length=0.001)+
    geom_bracket(y.position=0.28,xmin=1,xmax=3,label=post_hoc$p.adj.signif[2],tip.length=0.001)+
    geom_bracket(y.position=0.30,xmin=1,xmax=4,label=post_hoc$p.adj.signif[3],tip.length=0.001)



 ```

# distance effect anova:

 ```{r warning=FALSE}

 dat_dist <- dat %>% filter(ordered == FALSE)
plot_one_way(data=dat_dist,dep_var="dist_effect_ies_normed",indep_var="mode",y_label_to_use="distance effect (ies)")
ez_anova_res <- ezANOVA(data=dat_dist,dv=dist_effect_ies_normed,wid=prob_code,within=.(mode),return_aov=TRUE)
apa.ezANOVA.table(ez_anova_res)

pairwise.t.test(x=dat_dist$dist_effect_ies_normed, g=factor(dat_dist$mode), paired=TRUE, p.adjust.method="BH")
 ```


