---
title: "Analyse Gruppe 1"
params:
  hyp: rig
output:
  html_document: default
  pdf_document: default
---

## start by looking at the data:
 ```{r }
 library(PairedData)
 library(ggplot2)
 library(ggpubr)
 
 ```

 ```{r}
dat <- read.csv("data_with_dist_effect_1rpP.csv")
dat_all <-  read.csv("data_cleaned.csv")
dat_accuracy <-  read.csv("data_accuracy_part_mode.csv")

```

 ```{r }
ggdensity(dat_all, x = "rt_num",
   add = "mean", rug = TRUE,
   color = "mode", fill = "mode",
   palette = "jco")
 
 ```
 
 ```{r }
ggdensity(dat_accuracy, x = "accuracy",
   add = "mean", rug = TRUE,
   color = "mode", fill = "mode",
   palette = "jco")
 
 ```
 
  ```{r }
ggboxplot(dat_all, x = "mode", y = "rt_num",
                color = "mode", palette ="jco"
                , shape = "mode")
 
 ```

## distance effect:
Bei ungeordneten Zahlenfolgen werden kleinere Abstände langsamer identifiziert.

### single task
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.FALSE.single", cond2 = "mean_rt.2.FALSE.single",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
    
t.test(dat$mean_rt.1.FALSE.single,dat$mean_rt.2.FALSE.single,paired=TRUE,alternative="two.sided")
```
### dual phonological 
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.FALSE.dual_phon", cond2 = "mean_rt.2.FALSE.dual_phon",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$mean_rt.1.FALSE.dual_phon,dat$mean_rt.2.FALSE.dual_phon,paired=TRUE,alternative="two.sided")
```
### dual visual 
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.FALSE.dual_vis", cond2 = "mean_rt.2.FALSE.dual_vis",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$mean_rt.1.FALSE.dual_vis,dat$mean_rt.2.FALSE.dual_vis,paired=TRUE,alternative="two.sided")
```
### dual executive
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.FALSE.dual_rig", cond2 = "mean_rt.2.FALSE.dual_rig",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$mean_rt.1.FALSE.dual_rig,dat$mean_rt.2.FALSE.dual_rig,paired=TRUE,alternative="two.sided")
```



## reverse distance effect:
### single
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.TRUE.single", cond2 = "mean_rt.2.TRUE.single",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$mean_rt.1.TRUE.single,dat$mean_rt.2.TRUE.single,paired=TRUE,alternative="two.sided")
```
### dual phonological 
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.TRUE.dual_phon", cond2 = "mean_rt.2.TRUE.dual_phon",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$mean_rt.1.TRUE.dual_phon,dat$mean_rt.2.TRUE.dual_phon,paired=TRUE,alternative="two.sided")
```
### dual visual 
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.TRUE.dual_vis", cond2 = "mean_rt.2.TRUE.dual_vis",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$mean_rt.1.TRUE.dual_vis,dat$mean_rt.2.TRUE.dual_vis,paired=TRUE,alternative="two.sided")
```
### dual executive
 ```{r}
x_labels_to_use <- c("1","2")
ggpaired(dat, cond1 = "mean_rt.1.TRUE.dual_rig", cond2 = "mean_rt.2.TRUE.dual_rig",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Distanz"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$mean_rt.1.TRUE.dual_rig,dat$mean_rt.2.TRUE.dual_rig,paired=TRUE,alternative="two.sided")
```

## comparison of reverse distance effects:
### phon 
 ```{r}
x_labels_to_use <- c("single","dual phon")
ggpaired(dat, cond1 = "rev_dist_effect_normed.TRUE.single", cond2 = "rev_dist_effect_normed.TRUE.dual_phon",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Bedingung"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$rev_dist_effect_normed.TRUE.single,dat$rev_dist_effect_normed.TRUE.dual_phon,paired=TRUE,alternative="two.sided")
```

### vis 
 ```{r}
x_labels_to_use <- c("single","dual vis")
ggpaired(dat, cond1 = "rev_dist_effect_normed.TRUE.single", cond2 = "rev_dist_effect_normed.TRUE.dual_vis",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Bedingung"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$rev_dist_effect_normed.TRUE.single,dat$rev_dist_effect_normed.TRUE.dual_vis,paired=TRUE,alternative="two.sided")
```
### rig 
 ```{r}
x_labels_to_use <- c("single","dual rig")
ggpaired(dat, cond1 = "rev_dist_effect_normed.TRUE.single", cond2 = "rev_dist_effect_normed.TRUE.dual_rig",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Bedingung"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$rev_dist_effect_normed.TRUE.single,dat$rev_dist_effect_normed.TRUE.dual_rig,paired=TRUE,alternative="two.sided")
```



## comparison of distance effects:
### phon 
 ```{r}
x_labels_to_use <- c("single","dual phon")
ggpaired(dat, cond1 = "dist_effect.FALSE.single", cond2 = "dist_effect.FALSE.dual_phon",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Bedingung"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$dist_effect.FALSE.single,dat$dist_effect.FALSE.dual_phon,paired=TRUE,alternative="two.sided")
```

### vis 
 ```{r}
x_labels_to_use <- c("single","dual vis")
ggpaired(dat, cond1 = "dist_effect.FALSE.single", cond2 = "dist_effect.FALSE.dual_vis",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Bedingung"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$dist_effect.FALSE.single,dat$dist_effect.FALSE.dual_vis,paired=TRUE,alternative="two.sided")
```
### rig 
 ```{r}
x_labels_to_use <- c("single","dual rig")
ggpaired(dat, cond1 = "dist_effect.FALSE.single", cond2 = "dist_effect.FALSE.dual_rig",
    fill = "condition"
    , palette = "jco"
    ,line.size=0.1
    ,point.size=0.0
    ,width=0.5
    ,panel.labs = list(cond1="1",cond2="2")
    ,short.panel.labs=TRUE
    ,xlab= "Bedingung"
    ,ylab= "Reaktionszeit in s"
    ) + scale_x_discrete(labels=x_labels_to_use)
 
t.test(dat$dist_effect.FALSE.single,dat$dist_effect.FALSE.dual_rig,paired=TRUE,alternative="two.sided")
```






 ```{r echo=FALSE}

#### Rscript -e 'library(rmarkdown); rmarkdown::render("analysis.Rmd", "pdf_document",params = list(filename = "analysis.pdf"))'

```

 ```{r }

#dat <- read.csv("data_cleaned.csv")
#dat$prob_code <- factor(dat$prob_code)

#anova <- aov(rt_num ~ mode*distance*ordered #+Error(prob_code/(mode*distance*ordered)), data=dat)

#(anova)

#summary(anova)
```

 ```{r }
library(ez)
library(dplyr)

dat <- read.csv("data_cleaned.csv")

# TODO: remove participants completely.

dat <- dat %>% filter(!is.na(rt_num))
data_excluded <- read.csv("excluded_participants_p_mode.csv")
print(nrow(dat))
dat$distance <- as.factor(dat$distance)


#dat_incomplete <- dat %>% group_by(prob_code,distance,ordered,mode) %>% summarize(n = n(),na.rm=FALSE) %>% filter((!is.na(n)) &(n != 0)) 

#(dat_incomplete)
#dat <- dat %>% filter((prob_code %in% dat_incomplete$prob_code ))
  


#if(FALSE){
dat_true <- dat %>% filter((ordered == TRUE))
dat_false <- dat %>% filter((ordered == FALSE))

dat_true_1 <- dat_true %>% filter((distance == 1))
dat_false_1 <- dat_false %>% filter((distance == 1))
dat_true_2 <- dat_true %>% filter((distance == 2))
dat_false_2 <- dat_false %>% filter((distance == 2))


dat_true_1_single <- dat_true_1 %>% filter((mode == "single"))
dat_false_1_single <- dat_false_1 %>% filter((mode == "single"))
dat_true_2_single <- dat_true_2 %>% filter((mode == "single"))
dat_false_2_single <- dat_false_2 %>% filter((mode == "single"))

dat_true_1_dual_rig <- dat_true_1 %>% filter((mode == "dual_rig"))
dat_false_1_dual_rig <- dat_false_1 %>% filter((mode == "dual_rig"))
dat_true_2_dual_rig <- dat_true_2 %>% filter((mode == "dual_rig"))
dat_false_2_dual_rig <- dat_false_2 %>% filter((mode == "dual_rig"))

dat_true_1_dual_phon <- dat_true_1 %>% filter((mode == "dual_phon"))
dat_false_1_dual_phon <- dat_false_1 %>% filter((mode == "dual_phon"))
dat_true_2_dual_phon <- dat_true_2 %>% filter((mode == "dual_phon"))
dat_false_2_dual_phon <- dat_false_2 %>% filter((mode == "dual_phon"))

dat_true_1_dual_vis <- dat_true_1 %>% filter((mode == "dual_vis"))
dat_false_1_dual_vis <- dat_false_1 %>% filter((mode == "dual_vis"))
dat_true_2_dual_vis <- dat_true_2 %>% filter((mode == "dual_vis"))
dat_false_2_dual_vis <- dat_false_2 %>% filter((mode == "dual_vis"))

dat <- dat %>% filter((prob_code %in% dat_true_1_single$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_1_single$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_true_2_single$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_2_single$prob_code ))

dat <- dat %>% filter((prob_code %in% dat_true_1_dual_rig$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_1_dual_rig$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_true_2_dual_rig$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_2_dual_rig$prob_code ))

dat <- dat %>% filter((prob_code %in% dat_true_1_dual_phon$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_1_dual_phon$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_true_2_dual_phon$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_2_dual_phon$prob_code ))

dat <- dat %>% filter((prob_code %in% dat_true_1_dual_vis$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_1_dual_vis$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_true_2_dual_vis$prob_code ))
dat <- dat %>% filter((prob_code %in% dat_false_2_dual_vis$prob_code ))
#}



print(nrow(dat))

ez_aov <- ezANOVA(data=dat,dv=rt_num,wid=prob_code,within=.(distance,ordered,mode))
ez_aov
```

